---
title: "Iteration"
author: "Linh Tran"
date: "11/9/2020"
output: 
    html_document:
      toc: true
---

```{r}
library(tidyverse)
library(rvest)
```


# Writing Functions

## Do something simple 

e.g: z-score
```{r}
x_vec = rnorm(30, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

I want a funciton to compute z_scores

```{r} 
z_scores = function(x) {
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  z = (x - mean(x))/sd(x)
  return(z)
}

z_scores(x_vec)
```


## Multiple outputs

```{r}
mean_and_sd = function(x) {
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  mean_x = mean(x)
  sd_x = sd(x)
  
tibble(
    mean = mean_x,
    sd = sd_x
  )
}

# Check that the function works
mean_and_sd(x_vec)

#Update x_vec
x_vec = rnorm(1000)
mean_and_sd(x_vec)
```

## Multiple inputs

```{r}
sim_data = 
  tibble(
    x = rnorm(100, mean = 4, sd = 3)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```

I'd like to do this with a function

```{r}
sim_mean_sd = function(n , mu, sigma) {
  sim_data = 
  tibble(
    x = rnorm(n, mean = mu, sd = sigma)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
}

sim_mean_sd(100, 6, 3)
sim_mean_sd(n = 1000, mu = 20, sigma = 3)   # use name matching
```

## Let's review Napoleon Dynamite

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

What about the next page of reviews...

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews_page2 = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

Let's turn that code into a function

```{r}
read_page_reviews = function(url) {
  
  dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)

reviews

}

# Let's try function

dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=3"

read_page_reviews(dynamite_url)
```

Let's read a few pages of reviews

```{r}
dynamite_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

dynamite_url = str_c(dynamite_url_base, 1:5)

dynamite_url[1]
dynamite_url[2]

all_reviews = 
  bind_rows(
read_page_reviews(dynamite_url[1]),
read_page_reviews(dynamite_url[2]),
read_page_reviews(dynamite_url[3]),
read_page_reviews(dynamite_url[4]),
read_page_reviews(dynamite_url[5])
  )
```

## Mean scoping example 

```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```

## Functions as arguments

```{r}
my_summary = function(x, summ_func) {
  summ_func(x)
}

x_vec = rnorm(100, 3, 7)

mean(x_vec)
median(x_vec)

my_summary(x_vec, mean)
my_summary(x_vec, median)
my_summary(x_vec, IQR)
```

## Learning Assessment

```{r}
lotr_load_and_tidy = function(path, range, movie_name) {
  
  df = readxl::read_excel(path, range = range) %>%
    janitor::clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = str_to_lower(race),
           movie = movie_name)
  
  df
  
}

lotr_tidy = 
  bind_rows(
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "B3:D6", "fellowship_ring"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "F3:H6", "two_towers"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "J3:L6", "return_king")) %>%
  select(movie, everything()) 
```


# Iteration and list columns

## Lists

Example of lists
```{r}
list(a = rnorm(10), b = c("My", "name", "is", "Linh"), c = summary(runif(100)))
```

Data frame is a special kind of list

```{r}
data_frame(
  a = rnorm(4),
  b = c("My", "name", "is", "Linh"),
  c = sample(c(TRUE, FALSE), 4, replace = TRUE)
)
```

You can put anything in a list

```{r}
vec_numeric = 5:8
vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE)
matrix = matrix(1:8, nrow = 2, ncol = 4)
summary = summary(rnorm(100))

list(vec_numeric, vec_logical, matrix, summary)
```

```{r}
list = list(
 vec_numeric = 5:8,
 vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
 matrix = matrix(1:8, nrow = 2, ncol = 4),
 summary = summary(rnorm(100))
)

list
list$vec_logical
list$vec_numeric
list[[1]]
mean(list[["vec_numeric"]])

```

## `for` loop

Create a new list

```{r}
list_rnorm =
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(30, mean = 0, sd = 5),
    c = rnorm(40, mean = 10, sd = 0.2),
    d = rnorm(20, mean = -3, sd = 1)
  )

list_rnorm

```

I can apply mean and sd function to each list element

```{r}
mean_and_sd = function(x) {
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  mean_x = mean(x)
  sd_x = sd(x)
  
tibble(
    mean = mean_x,
    sd = sd_x
  )
}

mean_and_sd(list_rnorm[[1]])
mean_and_sd(list_rnorm[[2]])
mean_and_sd(list_rnorm[[3]])
mean_and_sd(list_rnorm[[4]])
```

Let's use a for loop:

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_rnorm[[i]])
}
```

## Let's try map

```{r}
output = map(list_rnorm, mean_and_sd)  #output = map(input, f)
```

What if you want a different function?

```{r}
map(list_rnorm, median)

map(list_rnorm, IQR)
```


# Simulation

